Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2018-10-24 awipev-CO2.Rmd
changement 2e read.table

#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "samir") path = "../pCloud\\ Sync/exp153_carbonates_point_B/"

@@

```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%",fig.show='hold', fig.align="center"}
calib_analyser <-  read.table("../fb_data/Calibration/TA_#1215/measure_CRM_TA.txt", header = T, dec = ".", as.is = T, sep = ",", fill = TRUE)

>>>>

#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"

@@

```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%",fig.show='hold', fig.align="center"}
calib_analyser <-  read.table(paste0(path, "fb_data/Calibration/TA_#1215/measure_CRM_TA.txt"), header = T, dec = ".", as.is = T, sep = ",", fill = TRUE)
